Stack Safety as a Security Property

### 2020-09-10 rebuttal.txt

By contrast, [Skorstengaard 2019b] relies on different prior intuitions: for
readers familiar with operational models of stacks (here the
built-in oLCM stack), their property is more intuitive. For readers
versed in security theory, we believe that making an explicit connection
with integrity and confidentiality gives useful insight.

(2) Usefulness for reasoning:

Local state encapsulation enables reasoning about the behavior of a
function in a vacuum, without needing to account for either its
caller's state or for changes to its state during its callees. When
proving a property of a function, confidentiality allows us to only
reason about configurations of the stack frame itself (instead of all
possible _memory_ configurations).  As for integrity, our threat model
permits a callee to execute arbitrary code, severely limiting our
ability to reason about the behavior of its caller after return. But
we can now prove properties of the caller by quantifying only over
configurations of registers and memory above the stack.

In security terms, we make no guarantees about the callee's behavior,
but we can guarantee that it communicates with the caller only through
the approved interface.  In terms of a logic, integrity and
confidentiality would allow a procedure rule that states that local
variables do not change over calls, (which basically says that
procedure calls are a no-op except for observations and the return value)
and that lemmas proved about procedure return values and observations can
be applied at call sites.

For a security-oriented example, suppose that a procedure f takes two
arguments, x and y, passes y on to a procedure g, and outputs the result. We
may wish to prove that x is not leaked - a noninterference proof that
for and x, x', and y, the output trace of f(x,y) is identical to that of
f(x',y). We would prove this easily for each step of f before the call to g;
at the call point, we would use confidentiality to claim that since the states
are variants of one another under the contour of g, they have the same
observable behavior and state changes if there is a return. Integrity guarantees
that at a return point, f's code has not changed. So, whatever value was returned
from g, it is output in both traces.

### 2020-09-10 rebuttal.txt

RELATED WORK

All reviewers also wanted additional discussion of related work.  We agree,
in particular, that there should be a clearer comparison to the two
Skorstengaard et al papers, using the five informal criteria proposed
there. We plan to include a discussion like the following:

(1) Intuitiveness:

The local state encapsulation (LSE) part of the property we present
aims to characterize stack safety in security terms. For readers
familiar with integrity / confidentiality / noninterference, the eager
version should be fairly intuitive. The lazy/observable properties,
though less intuitive, are more interesting in that they precisely
characterize behaviors that would be considered violations to the more
intuitive view of stack safety but that can still be considered safe
by an external observer. The well-bracketed control flow (WBCF) part
simply formalizes standard behavior of stack-based control flow.
